Are kelp forests different? A comparison of kelp forests between contrasting study sites

### 2018-07-11 paper_draft.Rmd
2nd commit.

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)

@@

```{r}

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x=id, y=species, colour = site, size =biomass)) +                   geom_point() + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("Species") + 
              xlab("ID")
```

ggplot(data = cover_long[which(cover_long$value>0),], aes(x=variable, y=value)) + geom_boxplot(notch = TRUE, varwidth = FALSE, aes(fill=Site), outlier.shape=NA, width = 0.3) + theme(axis.text.x=element_text(angle = 0, hjust = 0.5, vjust = 0.3)) + theme(panel.background = element_rect(fill = 'white', colour = 'grey'))+ xlab("") + ylab("%-cover") + ggtitle("") + scale_colour_brewer(palette = "Set2") + theme(aspect.ratio = 0.6)

>>>>

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)
library(gridExtra)

@@

```{r diversity graphs script, message=FALSE, warning=FALSE, paged.print=FALSE}

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x=id, y=species, colour = site, size =biomass)) +                   geom_point() + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("Species") + 
              xlab("ID")

ggsave("figures/fig1.png", grid.arrange(plot_flora, plot_fauna))
grid.arrange(plot_flora, plot_fauna, ncol=1)
```
